---
title: "WorkFlow"
author: "GenDoc94"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## OGM Read Workflow

Firstly, we have to pull all archives from our server (Dropbox) to our repository (OGMRead).

We should copy:

-   json_files

-   variants_files

-   aneuploidy_files

-   clinical_files

```{r copying_files}
source("copy_files.R")
```

If there is no error here, all is OK (no replicate Ids) we can proceed to the next step.

## Making the bases

Now, we are going to run the code to create the complete base.

```{r readfiles, echo=FALSE, message=FALSE, warning=FALSE}
source("read_files.R")
```

After this we have some bases:

-   complete_base -\> All the information about the patient and clinics

-   cb_filter -\> All the important variants of patients without LB/B variants.

And some subbases:

-   demograph

-   metadata

-   quality

-   variants

## Basics of our data

Here...

## Quality of Samples

Here...

## Generating Graphs

Finally, we can generate our circles plot:

```{r}
source("circleplot.R")
source("pdfgraphs.R")

# Generate PDF for MM
make_pdf_graphs(filter_dx = "MM", filename = "MM_graphs.pdf")

# Generate PDF for LMA
make_pdf_graphs(filter_dx = "LMA", filename = "LMA_graphs.pdf")

# Generate PDF for LLC
make_pdf_graphs(filter_dx = "LLC", filename = "LLC_graphs.pdf")
```
