---
title: "WorkFlow"
author: "GenDoc94"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(writexl)
library(gridExtra)
```

## OGM Read Workflow

Firstly, we have to pull all archives from our server (Dropbox) to our repository (OGMRead).

We should copy:

-   json_files

-   variants_files

-   aneuploidy_files

-   clinical_files

```{r copying_files}
source("copy_files.R")
```

If there is no error here, all is OK (no replicate Ids) we can proceed to the next step.

## Making the bases

Now, we are going to run the code to create the complete base.

```{r reading_files, echo=FALSE, message=FALSE, warning=FALSE}
source("read_files.R")
```

After this we have some bases:

-   complete_base -\> All the information about the patient and clinics

-   cb_filter -\> All the important variants of patients without LB/B variants and with some standard parameters: VAF > 0.05 and molecule count > 10.

And some subbases:

-   demograph

-   metadata

-   quality

-   variants

## Basics of our data

Here...

## Quality of Samples

Here...

```{r quality}
#TOTAL
quality |> 
        select(quantity, mol_n_50, coverage, map_rate, fp_rate, fn_rate) |>
        summary()

#By Patology
#Merge metadata+quality
qualmet <- left_join(quality, metadata, by = c("samplename" = "Id"))
#MM
qualmet |> filter(Dx == "MM") |>
        select(quantity, mol_n_50, coverage, map_rate, fp_rate, fn_rate) |>
        summary()
#LMA
qualmet |> filter(Dx == "LMA") |>
        select(quantity, mol_n_50, coverage, map_rate, fp_rate, fn_rate) |>
        summary()
#LLC
qualmet |> filter(Dx == "LLC") |>
        select(quantity, mol_n_50, coverage, map_rate, fp_rate, fn_rate) |>
        summary()

#Creating base 
qualmet_clean <- qualmet |> select(samplename, quantity, mol_n_50, coverage, map_rate, fp_rate, fn_rate, Dx)
```

## Generating list to export

```{r generating_export_list}
export_base <- complete_base |> select(Id, NHC, FechaNac, FechaPet, FechaDx, Petic, Dx)

#MM
export_base_MM <- export_base |> filter(Dx == "MM")
write_xlsx(export_base_MM, path = "export_base_MM.xlsx")
saveRDS(export_base_MM, "export_base_MM.rds")
rmarkdown::render("export_base_MM.Rmd")

#LMA
export_base_LMA <- export_base |> filter(Dx == "LMA")
write_xlsx(export_base_LMA, path = "export_base_LMA.xlsx")
saveRDS(export_base_LMA, "export_base_LMA.rds")
rmarkdown::render("export_base_LMA.Rmd")
```



## Generating Graphs

Finally, we can generate our circles plot:

```{r generating_circleplots}
source("circleplot.R") #This source generate the function circleplot(id_pac, dbase)
source("pdfgraphs.R") #This source generate the function make_pdf_graphs(filter_dx, filename)

# Generate PDF for MM
make_pdf_graphs(filter_dx = "MM", filename = "MM_graphs.pdf")

# Generate PDF for LMA
make_pdf_graphs(filter_dx = "LMA", filename = "LMA_graphs.pdf")

# Generate PDF for LLC
make_pdf_graphs(filter_dx = "LLC", filename = "LLC_graphs.pdf")
```
